---
title: "Top 1 Group Final Project"
author: "Hao Wang (haow12), Qiuning Ge (qiuning2), Chenhan Xu (chenhan2), and Zhongyu Wu (zhongyu6)"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output:
  html_document: 
    theme: cosmo
    toc: yes
  pdf_document: default
urlcolor: BrickRed
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE, warning = FALSE, fig.align = 'center')
```

```{r, load-packages, include = FALSE, message = FALSE}
library(dplyr)
library(caret)
library(purrr)
library(ggplot2)
library(knitr)
library(kableExtra)
library(tidyverse)
library(car)
library(randomForest)
library(car)
library(e1071)
```

```{r}
theme_set(theme_light())
```

***

# Abstract

> ABS

***

# Introduction

INTRO

***

# Methods

## Data

```{r}
bank = read.csv("bank-additional.csv")
```

```{r}
bank_full = read.csv("bank-additional-full.csv")
```

## Modeling

MODEL

### Evaluation

EVAL

### Binary Classification

CLASSIFICATION

***

# Results

RESULTS

***

# Discussion

DIS

***

# Appendix

## Data Dictionary

```{r, include = FALSE}
names(bank_trn)
```

- `age` - age in years
- `job` - type of job
- `marital` - marital status
- `education` - education level
- `default` - whether this client has credit in default
- `housing` - whether this client has housing loan
- `loan` - whether this client has personal loan
- `contact` - contact communication type
- `month` - last contact month of year
- `day_of_week` - last contact day of the week
- `duration` - last contact duration in seconds
- `campaign` - number of contacts performed during this campaign and for this client
- `pdays` - number of days that passed by after the client was last contacted from a previous campaign
- `previous` - number of contacts performed before this campaign and for this client
- `poutcome` - outcome of the previous marketing campaign
- `emp.var.rate` - employment variation rate
- `cons.price.idx` - consumer price index
- `cons.conf.idx` - consumer confidence index
- `euribor3m` - euribor 3 month rate
- `nr.employed` - number of employees
- `y` - whether the client has subscribed a term deposit?

See the UCI Machine Learning Repository for additional documentation.

## EDA

```{r}
plot_1 = bank_new %>%
  ggplot(aes(x = age, col = job)) + 
  geom_density()

plot_2 = bank_new %>%
  ggplot(aes(x = education, fill = education)) + 
  geom_bar() + 
  coord_flip() +
  facet_wrap(~housing)

plot_3 = bank_new %>%
  ggplot(aes(x = cons.conf.idx, y = cons.price.idx, color = y)) + 
  geom_point()

plot_4 = bank_new %>%
  ggplot(aes(x = age, col = loan)) + 
  geom_density()

plot_5 = bank_new %>%
  ggplot(aes(x = age, col = month)) + 
  geom_density()

plot_6 = bank_new %>%
  ggplot(aes(x = age, col = contact)) + 
  geom_density()

plot_7 = bank_new %>%
  ggplot(aes(x = y, fill = education)) + 
  geom_bar() + 
  facet_wrap(~job)

plot_8 = bank_new %>%
  ggplot(aes(x = education, fill = y)) + 
  geom_bar() +
  theme(axis.text.x = element_text(angle = 45))

plot_9 = bank_new %>%
  ggplot(aes(x = job, fill = y)) + 
  geom_bar() +
  theme(axis.text.x = element_text(angle = 45))

plot_10 = bank_new %>%
  ggplot(aes(x = previous, fill = y)) + 
  geom_bar()

plot_11 = bank_new %>%
  ggplot(aes(x = emp.var.rate, y = euribor3m)) +
  geom_point()

plot_12 = bank_new %>%
  ggplot(aes(x = emp.var.rate, y = nr.employed)) +
  geom_point()

plot_13 = bank_new %>%
  ggplot(aes(x = euribor3m, y = nr.employed)) +
  geom_point()
```

```{r, print-eda-plots, fig.height = 10, fig.width = 17}
gridExtra::grid.arrange(plot_1, plot_2, plot_3, plot_4, plot_5, plot_6, plot_7, plot_8, plot_9, plot_10)
```

```{r}
rf = randomForest(y ~ ., data = bank_full)
```

```{r}
rf$importance
```

```{r}
cor(bank_full[, c("emp.var.rate", "cons.price.idx", "euribor3m", "nr.employed")])
```

```{r pca}
pca = prcomp(bank_full[, c("emp.var.rate", "cons.price.idx", "cons.conf.idx", "euribor3m", "nr.employed")], center = TRUE, scale = TRUE)
# mat = scale(as.matrix(bank[, c("emp.var.rate", "cons.price.idx", "cons.conf.idx", "euribor3m", "nr.employed")]))
```

```{r pca scree}
evals = pca$sdev ^ 2
ggplot(mapping = aes(x = 1:length(pca$sdev), y = pca$sdev ^ 2 / sum(pca$sdev ^ 2))) +
  geom_line(color = "turquoise3", size = 1.5) + 
  geom_point(size = 5, color = "tomato", shape = 18) +
  xlab("Number of PCs") +
  ylab("Variance") + 
  ggtitle("Scree Plot")
```

```{r pca loading, fig.height = 7, fig.width = 7}
# function to create a circle
circle = function(center = c(0, 0), npoints = 100) {
    r = 1
    tt = seq(0, 2 * pi, length = npoints)
    xx = center[1] + r * cos(tt)
    yy = center[1] + r * sin(tt)
    return(data.frame(x = xx, y = yy))
}

corcir = circle(c(0, 0), npoints = 100)

# create data frame with correlations between variables and PCs
correlations = as.data.frame(cor(bank_full[, c("emp.var.rate", "cons.price.idx", "cons.conf.idx", "euribor3m", "nr.employed")], pca$x))

# data frame with arrows coordinates
arrows = data.frame(x1 = c(0, 0, 0, 0, 0), y1 = c(0, 0, 0, 0, 0), x2 = correlations$PC1, 
    y2 = correlations$PC2)

# geom_path will do open circles
ggplot() +
  geom_path(data = corcir, aes(x = x, y = y), colour = "turquoise3") + 
  geom_segment(data = arrows, aes(x = x1, y = y1, xend = x2, yend = y2), colour = "turquoise3") + 
  geom_text(data = correlations, aes(x = PC1, y = PC2, label = rownames(correlations)), color = "tomato") + 
  geom_hline(yintercept = 0, colour = "gray65") +
  geom_vline(xintercept = 0, colour = "gray65") +
  xlim(-1.1, 1.1) +
  ylim(-1.1, 1.1) +
  labs(x = "pc1 aixs", y = "pc2 axis") +
  ggtitle("Circle of correlations")
```

```{r transform}
bank_new_full = bank_full %>%
  filter(
      bank_full$job != "unknown" &
      bank_full$marital != "unknown" &
      bank_full$education != "unknown" &
      bank_full$loan != "unknown" & bank_full$housing != "unknown") %>%
  select(-c("cons.price.idx", "euribor3m", "nr.employed"))
bank_new = bank %>%
  filter(
      bank$job != "unknown" &
      bank$marital != "unknown" &
      bank$education != "unknown" &
      bank$loan != "unknown" & bank$housing != "unknown") %>%
  select(-c("cons.price.idx", "euribor3m", "nr.employed"))
```

```{r}
#set.seed(42)
idx = createDataPartition(bank_new$y, p = 0.8, list = FALSE)
bank_trn = bank_new[idx, ]
bank_tst = bank_new[-idx, ]
idx = createDataPartition(bank_new_full$y, p = 0.8, list = FALSE)
bank_trn_full = bank_new_full[idx, ]
bank_tst_full = bank_new_full[-idx, ]
```

```{r}
names(bank_new)
```

```{r}
levels(bank_new_full$marital)
```

```{r}
bank_trn_full_x = model.matrix(y ~ ., data = bank_trn_full)[, -1]
bank_tst_full_x = model.matrix(y ~ ., data = bank_tst_full)[, -1]
```

```{r}
nb1 = train(y ~ ., data = bank_trn_full, method = "naive_bayes", tuneLength = 20,
           trControl = trainControl(method = "cv", num = 5, sampling = "up",
                                    classProbs = TRUE,
                                    summaryFunction = twoClassSummary),
           metric = "Sens")
```

```{r}
cm1 = confusionMatrix(predict(nb1, bank_tst_full, type = "raw"), bank_tst_full$y, positive = "no")
```

```{r}
mod_nb = train(y ~ ., data = bank_trn_full, method = "naive_bayes", tuneLength = 20,
           trControl = trainControl(method = "cv", num = 5,
                                    classProbs = TRUE,
                                    summaryFunction = twoClassSummary),
           metric = "ROC")
```

```{r}
cm_nb = confusionMatrix(predict(mod_nb, bank_tst_full, type = "raw"), bank_tst_full$y, positive = "no")
```

```{r}
mod_nb_smote = train(y ~ ., data = bank_trn_full, method = "naive_bayes", tuneLength = 20,
           trControl = trainControl(method = "cv", num = 5, sampling = "smote",
                                    classProbs = TRUE,
                                    summaryFunction = twoClassSummary),
           metric = "ROC")
```

```{r}
cm_nb_smote = confusionMatrix(predict(mod_nb_smote, bank_tst_full, type = "raw"), bank_tst_full$y, positive = "no")
```

```{r}
nb4 = train(y ~ ., data = bank_trn_full, method = "naive_bayes", tuneLength = 20,
           trControl = trainControl(method = "cv", num = 5, sampling = "up",
                                    classProbs = TRUE,
                                    summaryFunction = twoClassSummary),
           metric = "ROC")
```

```{r}
cm4 = confusionMatrix(predict(nb4, bank_tst_full, type = "raw"), bank_tst_full$y, positive = "no")
```

##############################################

```{r}
library(glmnet)

bank_trn_full_x = model.matrix(y ~ ., data = bank_trn_full)[, -1]
bank_tst_full_x = model.matrix(y ~ ., data = bank_tst_full)[, -1]

cv.modelfull_lasso = cv.glmnet(bank_trn_full_x, as.numeric(bank_trn_full$y), alpha=1, family = "binomial")

pred = as.factor(ifelse(predict(cv.modelfull_lasso, bank_tst_full_x, type = "response") > 0.5, "yes", "no"))

confusionMatrix(data = pred, reference = bank_tst_full$y, positive = "yes")
```

#####################################################

```{r, cv-control-binary}
cv_binary = trainControl(
  method = "cv",
  number = 5,
  classProbs = TRUE,
  summaryFunction = twoClassSummary)

cv_binary_up = trainControl(
  method = "cv",
  number = 5,
  classProbs = TRUE,
  summaryFunction = twoClassSummary,
  sampling = "up")
```

```{r, echo = TRUE}
set.seed(42)
rf_mod = train(
  form = y ~ ., 
  data = bank_trn,
  method = "ranger",
  trControl = cv_binary,
  metric = "ROC",
  tuneLength = 20
)
```

```{r, echo = TRUE}
set.seed(42)
rf_mod_up = train(
  form = y ~ ., 
  data = bank_trn,
  method = "ranger",
  trControl = cv_binary_up,
  metric = "ROC",
  tuneLength = 20
)
```

```{r}
confusionMatrix(data = predict(rf_mod, bank_tst, type = "raw"),
                reference = bank_tst$y,
                positive = "no")
```

```{r}
confusionMatrix(data = predict(rf_mod_up, bank_tst, type = "raw"),
                reference = bank_tst$y,
                positive = "yes")
```

```{r}
cv_binary_oob = trainControl(
  method = "oob")

cv_binary_oob_up = trainControl(
  method = "oob",
  sampling = "up")
```

```{r}
set.seed(42)
rf_mod_oob = train(
  form = y ~ ., 
  data = bank_trn,
  method = "ranger",
  trControl = cv_binary_oob,
  tuneLength = 20
)
```

```{r}
confusionMatrix(data = predict(bin_mod_rf_oob, bank_tst, type = "raw"),
                reference = bank_tst$y,
                positive = "yes")
```

```{r}
set.seed(42)
bin_mod_rf_oob_up = train(
  form = y ~ ., 
  data = bank_trn,
  method = "ranger",
  trControl = cv_binary_oob_up,
  tuneLength = 20
)
```

```{r}
confusionMatrix(data = predict(bin_mod_rf_oob_up, bank_tst, type = "raw"),
                reference = bank_tst$y,
                positive = "yes")
```

##############################################


```{r samping = up, metric = roc}
set.seed(42)
ctrl <- trainControl(method="cv",
                     number = 5, 
                     sampling = "up",
                     classProbs=TRUE,
                     summaryFunction = twoClassSummary
                     )
knnFit4 <- train(y ~ ., data = bank_trn, 
                method = "knn", 
                trControl = ctrl, 
                metric = "ROC",
                preProcess = c("center","scale"),
                tuneLength = 20)
knnFit4

confusionMatrix(data = predict(knnFit4, bank_tst), 
                    reference = bank_tst$y, positive = "no")
```

```{r up_sampling, accuracy}
set.seed(42)
ctrl <- trainControl(method="cv",
                     number = 5, 
                     sampling = "up"
                     #classProbs=TRUE,
                     #summaryFunction = twoClassSummary
                     )
knnFit2 <- train(y ~ ., data = bank_trn, 
                method = "knn", 
                trControl = ctrl, 
                preProcess = c("center","scale"),
                tuneLength = 20)
knnFit2

confusionMatrix(data = predict(knnFit2, bank_tst), 
                    reference = bank_tst$y, positive = "no")
```

```{r, sampling = smote, accuracy}
set.seed(42)
ctrl <- trainControl(method="cv",
                     number = 5, 
                     sampling = "smote"
                     #classProbs = TRUE,
                     #summaryFunction = twoClassSummary
                     )
knnFit5 <- train(y ~ ., data = bank_trn, 
                method = "knn", 
                trControl = ctrl,
                preProcess = c("center","scale"),
                tuneLength = 20)
knnFit5


confusionMatrix(data = predict(knnFit5, bank_tst), 
                    reference = bank_tst$y, positive = "no")
```

```{r, no sampling, accuracy}
set.seed(42)
ctrl <- trainControl(method="cv",
                     number = 5
                     #sampling = "smote"
                     #classProbs = TRUE,
                     #summaryFunction = twoClassSummary
                     )
knnFit6 <- train(y ~ ., data = bank_trn, 
                method = "knn", 
                trControl = ctrl,
                preProcess = c("center","scale"),
                tuneLength = 20)
knnFit6


confusionMatrix(data = predict(knnFit6, bank_tst), 
                    reference = bank_tst$y, positive = "no")
```

